% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{xcolor}

\usepackage{comment}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    pdftitle={CV_Islam},
    pdfpagemode=FullScreen,
    anchorcolor = blue]{hyperref}
    }

\usepackage{geometry}
\usepackage{supertabular} 				%for Grades
\usepackage[utf8]{inputenc}
%\usepackage[a4paper,margin=1in]{geometry}

%tabularx environment
\usepackage{tabularx}

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\looseness=-1


% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Md Johirul Islam}



% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = blue,
  linkcolor=blue,
  filecolor=blue,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=.8in,
  top=1in,
  right=1in,
  bottom=1in
}

 %Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.55\linewidth}
BRAC Institute of Governance and Development(BIGD)\\
BRAC Tower 65, Bir Uttam AK Khandakar Road \\
Mohakhali, Dhaka 1212, Bangladesh \\
\end{minipage}
\begin{minipage}{0.4\linewidth}
  \begin{tabular}{ll}
    Phone:   & +8801733596903 \\
    LinkedIn:& www.linkedin.com/in/pappu97cu \\
    Email:   & johirul.islam.cu@gmail.com \\
    Website: & https://mjohirulislam.github.io \\
    GitHub: & https://github.com/mjohirulislam \\
   Twitter: &  https://twitter.com/johir\_econ \\

  \end{tabular}
\end{minipage}


\section*{Educations}


\begin{tabular}{p{4.5in}r}
	\textbf{M.S., Mathematics, Ahsanullah University of Science and Technology} & \textbf{March 2024--Current} \\
	\noalign{\vskip 0.4\baselineskip}
	\textit{Relevant Courses:} Ordinary Differential Equations, Advanced Topics in Optimization, Graph Theory, Advanced Calculus, Numerical Analysis, Probability, Stochastic Processes and Applications I& \\
	\textbf{CGPA:} 3.92/4.00 (Till second semester) & \\
	\\
	\textbf{B.S.S., Economics, University of Chittagong} & \textbf{January 2017--August 2022} \\
	\noalign{\vskip 0.4\baselineskip}
	\textit{Relevant Courses:} Microeconomic Theory I, Microeconomic Theory II, Macroeconomic Theory I, Macroeconomic Theory II, Mathematics for Economists, Mathematics for Economists II, Mathematical Economics, Statistics for Economists I, Statistics for Economists II, and Econometrics.& \\
	\textbf{CGPA:} 3.46/4.00 (Last year GPA: 3.68) & \\
\end{tabular}



\section*{Experiences}
\subsection*{\bf Research Experiences}

\subsection*{Senior Research Associate (SRA)  \hfill \normalsize (July 2025-current)}
{\it BRAC Insitute of Governance and Development (BIGD), Brac University}
\begin{itemize}
	\item Responsible for study design, survey development, enumerator training, survey management, data analysis, and report writing. Leading an RCT on child marriage and education in crisis contexts.
\end{itemize}

\subsection*{Research Associate (RA)  \hfill \normalsize (December 2022-June 2025)}
{\it BRAC Insitute of Governance and Development (BIGD), Brac University}
\begin{itemize}
\item Responsibilities include designing research studies, developing questionnaires and survey form, training enumerators, managing survey operations, coordinating with stakeholders, cleaning and validating data, analyzing datasets, creating tables and graphs, and writing reports, blogs, research papers, and proposals.
\end{itemize}

\subsection*{Research Assistant (RA) (part-time remote) \hfill \normalsize (November 2023-November 2024)}
{ \it Department of International Development, London School of Economics (LSE)}
\begin{itemize}
\item Assisted Dr. Naila Kabeer, Professor of Gender and Development, by cleaning and analyzing data, and creating tables and graphs for various projects in Bangladesh and India
\end{itemize}

\subsection*{Trainee Research Associate (TRA)  \hfill \normalsize (June 2022- December 2022)}
{\it BRAC Insitute of Governance and Development (BIGD), Brac University}
\begin{itemize}
\item Responsibilities include designing questionnaire, managing survey, cleaning and validating data, analyzing data, creating tables and graphs.
\end{itemize}

\subsection*{Research Assistant (RA) (part-time) \hfill \normalsize (May-June 2022)}
{ \it Department of Economics, University of Chittagong}
\begin{itemize}
\item Assistant to Ms. Tonmoyee Hasan Ayon, assisting in survey analysis and writing graphical illustration on the project named "Demography of Housemaids and Rickshaw pullers during Covid-19".
\end{itemize}




\subsection*{\bf Teaching Experiences}

\subsection*{Teaching Assistant (TA) (part-time) at BIGD, Brac University, Bangladesh \hfill \normalsize (June 2023- current)}
\begin{itemize}
\item  Assist Dr. Munshi Sulaiman in distributing lecture notes, grading exam papers, preparing lectures, etc., for {\it DEV 502 Poverty: Concept, Measurement and Policy} course offered in Master of Development Studies
\end{itemize}



\section*{Researchs}

\subsection*{Publications}
\begin{enumerate}
	\item {\bf Islam, M. J.}, Hossain, M., \& Haque, S. T. (2025). The cost of discipline? Exploring the impact of corporal punishment on children’s foundational learning skills in Bangladesh. {\it International Journal of Educational Development}, 117, 103360. \href{https://doi.org/10.1016/j.ijedudev.2025.103360}{[Link]} 
\end{enumerate}


\subsection*{Working Papers}
\begin{enumerate}

\item Behind Closed Doors: Corporal Punishment at Home and Its Consequences for Emotional Regulation in Children-An Instrumental Variable Approach with Arishfa Nawar Iqra and Md. Robiul Hossain, \textit{Under review at Child Abuse \& Neglect}

\item Perception vs. Reality: Daughter's Social Media Use and Elopement Concerns Among Parents in Rural Bangladesh with Munshi Sulaiman and Shaila Ahmed

\item Belief Measurement: The Role of Survey Incentives with Atiya Rahman

\item Women’s Property Rights and Fertility: Cross-Country Evidence with Shaila Ahmed, Akmam Binte Arif, and Sheikh Touhidul Haque

\item Does Hunger Affect Violent Crime? A Cross-Country Study of Developing Nations with Naim Hasan Chy. Available at SSRN: \href{https://ssrn.com/abstract=4033213 }{[Link]} 


\end{enumerate}

\subsection*{Selected Works-In-Progress}
\begin{enumerate}
\item Optimizing Cash Transfers with Social Empowerment Interventions to Reduce Child Marriage in Bangladesh with Munshi Sulaiman, Shaila Ahmed,  Khandker Wahedur Rahman, and Sakib Mahmud. \href
{https://doi.org/10.1257/rct.13652-1.0}{AEA RCT Registry}


\item Play-Based Learning in Crisis Contexts: A Randomized Controlled Trial on Educational and Psychosocial Outcomes in Host Community Children with Shaila Ahmed, Justine Howard, Sakila Yesmin, Muhammad Towkir Hossain. \href
{https://www.socialscienceregistry.org/trials/15577/history/261715}{AEA RCT Registry}

\end{enumerate}

\subsection*{Policy Writings/Reports}
\begin{enumerate}

\item “Partnership for Research on Progress and Resilience in Education (PREPARE): Round 1 Policy Brief” with Marjan Hossain, Khandker Wahedur Rahman, and Shaila Ahmed. 2023. BRAC Institute of Governance and Development (BIGD) Report. Dhaka, Bangladesh. \href{https://bigd.bracu.ac.bd/wp-content/uploads/2023/06/PREPARE_RB_06062023.pdf}{[PDF]}


\end{enumerate}


\subsection*{Blog Posts}

\begin{enumerate}

\item \href{https://www.cgdev.org/blog/unravelling-association-between-shocks-and-education-bangladesh}{"Unravelling the Association between Shocks and Education in Bangladesh",} with  Marjan Hossain, Radhika Nagesh, Shaila Ahmed, and Khandker Wahedur Rahman. Center for Global Development, July 11, 2023. 

\item \href{https://www.cgdev.org/blog/learning-crisis-persists-bangladesh-findings-two-stage-study}{The Learning Crisis Persists in Bangladesh: Findings from a Two-stage Study",} with  Marjan Hossain, Radhika Nagesh, Shaila Ahmed, and Khandker Wahedur Rahman. Center for Global Development, Nov 29, 2023. 


\end{enumerate}

\begin{comment}
\subsection*{Research Projects}\footnote{Star (*) means I'm one of the Co-PI's of the project. Two stars (**) mean I oversee the project. No stars mean I work/worked as RA for the project.}

\indent Completed 

\begin{enumerate}

\item Validation of ASER Assessment Tool: Phone vs In-person (2022)

\item Partnership for Research on Progress and Resilience in Education (PREPARE) Bangladesh Round I and II in collaboration with Centre for Global Development (CGD) Europe (2023)

\item Evaluation of Positive Parenting for Adolescents Pilot in collaboration with the Centre for Global Development (CGD)

\end{enumerate}


\indent Ongoing

\begin{enumerate}

\item Randomized Controlled Trial (RCT) Study on Social Norms and Child Marriage: Impact Evaluation of BRAC's SELP Program.* 


\item Education Research in Conflict and Crisis: Bilateral Research Chairs in Collaboration with British Academy**

\item Randomized Controlled Trial (RCT) Study on Evidence on Childcare (ECC) funded by Bill and Melinda Gates Foundation (BMGF)**


\end{enumerate}


\end{comment}

\section*{Skills}
\begin{itemize}
   \item Programming: STATA (advance),  R (Intermediate), Python (Intermediate), \LaTeX\  (advance), Matlab (basic)
  
  \item Professional: Google Workspace, Microsoft Office Suite,  Adobe Photoshop (Basic), Adobe Premiere Pro (Intermediate), Adobe Illustrator (Basic)
  \item Developer Tools: VS Code, GitHub
  \item Others: HTML, CSS, Markdown, Canva, ArcGIS (basic), SurveyCTO (intermediate)
  \item Languages: Bangla (native), English (fluent), Hindi (Basic)
\end{itemize}



\section*{Research Interests}
\begin{minipage}{0.5\linewidth} 
\subsection*{Primary Interests}
\begin{itemize}
\item Development Economics
\item Behavioral Economics

\end{itemize}
\end{minipage}
\begin{minipage}{0.5\linewidth}

\subsection*{Secondary Interests}
\begin{itemize}
\item Experimental Economics
\item Economics of Education

\end{itemize}

\end{minipage}



\section*{Leaderships and Co-curricular Activities}

\begin{itemize}
\item {\bf Policy Enovy} at Youth Policy Forum, Bangladesh \hfill \normalsize (2021-2022)
\item {\bf Member} at Youth Ending Hunger Bangladesh \hfill \normalsize (2017-18).
\item {\bf Youth Leader} at Active Citizens-British Council \hfill \normalsize (2017-2018).
\item {\bf Volunteer} at The Hunger Project \hfill \normalsize (2017-18).
\item { \bf Executive Member} at Young Economists Society, CU. \hfill \normalsize (2019)
\end{itemize}



\begin{comment}

\section*{Courses and Accomplishments}

\begin{itemize}
\item December 15, 2022: "Hands-on training on applied quantitative research methods in development economics" under the Young Researchers' Fellowship program, BIGD, Brac University, the six-month long training covered contents such as Basic Economterics, Applied Econometrics, Advanced Training in Stata, Basic Sampling, Survey Instrument Development, Survey CTO Training, Research Communications, Research Ethics and Academic Writing. 


\item May 9, 2022: "Introduction to Psychology", Yale University, (via Coursera), learned about foundational psychological theories, child development and language, cognition, examining the self and others, human variation, mental illness and therapies, and measures of happiness (with certificate).

\item September 2021: "Causal Inference", Baylor University and Remote Student Exchange Program, instructed by Dr. Scott Cunningham, taught topics on Hidden Curriculum, Potential Outcome Model, Regression Discontinuity, IVs, DAG, DiD, and Synthetic Control etc.  (with Certificate)

\item March 2021: "ECON 2338 - Behavioral Development Economics", Harvard University and Remote Student Exchange Program, instructed by Dr. Gautam Rao, the class provided training in empirical methods and introduces new topics on the behavioral science of poverty and covered innovative applications of behavioral economics to development research, and highlights ideas which could be particularly ripe for application to development questions.  (participated as a silent auditor)

 \item February 9, 2021: "Framework for Data Collection and Analysis", University of Maryland, College Park (via Coursera), giving an introduction on framework for data collection and analysis (with certificate).
\end{itemize}


\end{comment}

\section*{Conferences and Presentations}
\begin{itemize}
	
	\item {\bf Islam, Md Johirul}, Iqra, Arishfa Nawar, Hossain, Md. Robiul. Behind Closed Doors: Corporal Punishment at Home and Its Consequences for Emotional Regulation in Children—An Instrumental Variable Approach. Presented at the Fifth Annual International Conference:\textbf{ A New Global Order, Yet Again;} IBA Center for Business \& Economic Research (CBER); November 14, 2025; Karachi, Pakistan (Online).
	
	\item {\bf Islam, Md Johirul}, Chy, Naim Hasan. Does hunger affect violent crime? A cross-country study of developing nationas. Poster is presented at the 1st research symposium organised by the Institutional Quality Assurance Cell (IQAC) of the University of Chittagong; March 24, 2022; Chittagong, Bangladesh. 
	
	\item {\bf Islam, Md Johirul}, Chy, Naim Hasan. Does hunger affect violent crime? A cross-country study
	of developing nationas. Poster is presented at 1st national Jamal Nazrul Islam national conference
	organized by CUHRS and Jamal Nazrul Islam Mathematical and Physical Sciences Institute, University
	of Chittagong ; May 21, 2022; Chittagong, Bangladesh.
	
	
	
\end{itemize}


\section*{Workshops \& Certifications}
\begin{itemize}

\item August 25-30, 2024, {\bf Research Staff Training 2024}, hosted by J-PAL South Asia in Goa, India

\item December 15, 2022: {\bf "Hands-on training on applied quantitative research methods in development economics"} under the Young Researchers' Fellowship program, BIGD, Brac University, the six-month long training covered contents such as Basic Economterics, Applied Econometrics, Advanced Training in Stata, Basic Sampling, Survey Instrument Development, Survey CTO Training, Research Communications, Research Ethics and Academic Writing. 

\item September 2021: {\bf "Causal Inference"}, Baylor University and Remote Student Exchange Program, instructed by Dr. Scott Cunningham, taught topics on Hidden Curriculum, Potential Outcome Model, Regression Discontinuity, IVs, DAG, DiD, and Synthetic Control etc.

\item March 2021: \textbf{"ECON 2338 - Behavioral Development Economics"}, Harvard University and Remote Student Exchange Program, instructed by Dr. Gautam Rao, the class provided training in empirical methods and introduces new topics on the behavioral science of poverty and covered innovative applications of behavioral economics to development research, and highlights ideas which could be particularly ripe for application to development questions.  (participated as a silent auditor)

\end{itemize}



\section*{Awards and Honors}
\begin{itemize}

\item {\bf Young Researchers' Fellowship (YRF) 2022}, BIGD, Brac University \hfill \normalsize (June, 2022)

\item {\bf The Champion} as a team in the category of {\it Best Social Action Project} in Active Citizens Regional Achievers Summit 2018 organized by Active Citizens-British Council.
\end{itemize}




\section*{References}
\begin{minipage}{0.33\linewidth}
Dr. Munshi Sulaiman\\
{\it Research Director and Professor \\
BIGD, Brac University \\
Dhaka, Bangladesh\\
Email: munshi.sulaiman@bracu.ac.bd}
\end{minipage}
\begin{minipage}{0.5\linewidth}
Dr. Khandker Wahedur Rahman \\
{\it Senior Postdoctoral Researcher, \\
University of Oxford, \\
34 Broad Street,OX1 3BD, United Kingdom \\
Email: khandkerwahedur.rahman@oxfordmartin.ox.ac.uk}
\end{minipage}
\begin{minipage}{0.4\linewidth}
	Dr. Md. Alauddin Majumder \\
	{\it Professor of Economics\\
		University of Chittagong\\
		Chittagong 4331, Bangladesh\\
		Email: ecoalauddin@cu.ac.bd}
\end{minipage}





% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
 
  \end{footnotesize}
\end{center}

\end{document}